Epilepsy example

### 2022-11-07 src/epil/epil.Rmd
Render epil

obj_fixed_theta <- MakeADFun(
  data = dat,
  parameters = param_fixed_theta,
  random = get_random(dat),
  DLL = "epil_index",
  silent = TRUE,
  map = map_fixed_theta
)

quad <- aghq::aghq(
  ff = obj_fixed_theta,
  k = 3,
  startingvalue = 0,
  control = aghq::default_control_tmb()
)

pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad, finegrid = finegrid)[[1]]

```

>>>>

# obj_fixed_theta <- MakeADFun(
#   data = dat,
#   parameters = param_fixed_theta,
#   random = get_random(dat),
#   DLL = "epil_index",
#   silent = TRUE,
#   map = map_fixed_theta
# )
#   
# quad <- aghq::aghq(
#   ff = obj_fixed_theta,
#   k = 3,
#   startingvalue = 0,
#   control = aghq::default_control_tmb()
# )
# 
# pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad, finegrid = finegrid)[[1]]
```
